19Q2

### 2020-01-14 19Q2.Rmd

```{r pancan_ks_res}
pancan_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
  "p.value" = c(ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)$p.value))
```

@@

test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test3 <- filter(cn_cor, Gene == "MET" & InG2P == "Yes")
```

>>>>

```{r pancan_ks_res, eval=FALSE}
pancan_ks_results <- data.frame("Dataset" = c(rep(c("CCLE", "CTRP", "GDSC"), 4)),
           "Data type" = c(rep("Mutation", 3), rep("Protein change", 3), rep("Copy number", 3), rep("Gene expression", 3)),
  "p.value" = c(ks.test(filter(ccle_mut_ht_dat, InG2P == "Yes")$p, filter(ccle_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_mut_ht_dat, InG2P == "Yes")$p, filter(ctrp_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_mut_ht_dat, InG2P == "Yes")$p, filter(gdsc_mut_ht_dat, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_prot_ht_data, InG2P == "Yes")$p, filter(ccle_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ctrp_prot_ht_data, InG2P == "Yes")$p, filter(ctrp_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(gdsc_prot_ht_data, InG2P == "Yes")$p, filter(gdsc_prot_ht_data, InG2P == "No")$p)$p.value,
  ks.test(filter(ccle_cn_ht_data, InG2P == "Yes")$CN_p, filter(ccle_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ctrp_cn_ht_data, InG2P == "Yes")$CN_p, filter(ctrp_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(gdsc_cn_ht_data, InG2P == "Yes")$CN_p, filter(gdsc_cn_ht_data, InG2P == "No")$CN_p)$p.value,
  ks.test(filter(ccle_ge_ht_data, InG2P == "Yes")$GE_p, filter(ccle_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(ctrp_ge_ht_data, InG2P == "Yes")$GE_p, filter(ctrp_ge_ht_data, InG2P == "No")$GE_p)$p.value,
  ks.test(filter(gdsc_ge_ht_data, InG2P == "Yes")$GE_p, filter(gdsc_ge_ht_data, InG2P == "No")$GE_p)$p.value))
```

@@

test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test3 <- filter(cn_cor, Gene == "MET" & InG2P == "Yes")

test <- filter(ge_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
test2 <- filter(cn_cor_lin, Drug != "CRISPR" & InG2P == "Yes")
```
